### 2018-05-17 paper/paper.tex
paper edits and comments

\newcommand{\jt}[1]{\textbf{\color{blue}JT: #1}}

@@

There were 26-32 certainty ratings for each of the 59 NEAS (mean: 28.5), except for the five NEASs that appeared on two lists, for which there were 52-58 certainty ratings each (mean: 54). We calculated the mean certainty rating of the prejacent of each NEAS: the lowest mean certainty rating was 1.2, the highest was 6.7 and the mean certainty rating overall was 3.2. Given that participants gave their ratings on a 7-point scale, with the lowest rating (1) indicating that the speaker was not certain about the relevant content and the highest rating (7) indicating that the speaker was certain about the relevant content, this mean certainty rating already suggests that the prejacent of naturally occurring NEAS is not highly projective. Figure \ref{f-corpus} shows the mean certainty ratings of each NEAS by evaluative adjective; darker dots indicate overlapping means. The distribution of mean certainty ratings again suggests that the prejacent of naturally occurring NEAS is projective, but not highly so, and that NEAS in which the prejacent does not project are well-attested in naturally occurring data. These findings provide empirical support for an analysis according to which the prejacent is not lexically specified as a presupposition.

@@

\caption{Mean certainty rating of 59 naturally occurring NEASs by evaluative adjective. Darker dots indicate overlapping means.}\label{f-corpus}

@@

\begin{exe}
\ex\label{xbox} I was stupid to buy the xbox 360 elite.\footnote{\url{www.gamespot.com/forums/xbox-association-1000003/i-was-stupid-to-buy-the-xbox-360-elite-26937557}}
\end{exe}

@@

\end{exe}
In the next section, we provide empirical evidence for the analysis.

\section{Empirical evidence for the analysis}\label{s4}

This section provides empirical evidence for the analysis of EASs developed in the previous section. In particular, we show that three predictions of the analysis, given in (\ref{pred}), are borne out: the prediction in (\ref{pred}a) is derived from (\ref{cq-eval}a), and the predictions in (\ref{pred}b) and (\ref{pred}c) are derived from (\ref{cq-eval}b).

@@

Next we consider examples of NEASs in which the prejacent does not project. Two of the prosodic realization of EASs considered in section \ref{s3331} were such that the EASs have Current Questions that are compatible with Discourse Questions according to which the prejacent is at-issue and therefore does not project: focus on the subject noun phrase and focus on the {\em to}-infinitive. In the examples in (\ref{subj}), the subject noun phrases are plausibly understood to be contrastively focused. A particularly clear example is (\ref{subj}a) where the speaker contrasts themselves with the uncle. Another clear example is (\ref{subj}b): here, {\em either} establishes a contrast between the Google founders and the federal government.

@@

\subsection{Experiment 1: Projectivity of the prejacent}\label{s42}

This section provides experimental evidence for the prediction of our analysis in (\ref{pred}b): the stronger the inference to the truth of the generalization from world knowledge, the less projective is the prejacent.

@@

\caption{Mean projectivity rating for prejacents of NEAS with the 10 evaluative adjectivesin the Content condition (left panels) and the Context condition (right panels) by whether the generalization or its negation follow from the common ground. Error bars indicate bootstrapped 95\% confidence intervals.}\label{f-condis}
\end{center}
\end{figure}

We fitted ordinal mixed-effects regression models to the target data in the Content and Context conditions (668 and 672 data points, respectively), using the {\tt clmm} function of the {\tt ordinal} package (\citealt{Christensen2013}) in {\em R} (\citealt{r}; version 3.2.0). The models predicted projectivity ratings on the 7-point Likert scale from the fixed effect of the discourse status of the generalization (with `generalization follows' as the reference level). The model included the maximal random effects structure justified by the data and the theoretical assumptions: random by-participant intercepts (capturing differences in projectivity between participants) and random by-adjective intercepts (capturing differences in projectivity between evaluative adjectives) and random slopes for the discourse status of the generalization by participant and adjective (capturing that the effect of the discourse status may vary across participants and adjectives). Here and in the remainder of the paper, $p$-values were obtained by comparing models with a likelihood ratio test.

@@

\subsection{Experiment 2: At-issueness of the prejacent}\label{s43}

This section provides experimental evidence for the prediction in (\ref{pred}c): the stronger the inference to the truth of the generalization from the common ground, the more at-issue is the prejacent. This prediction is explored on the basis of participants' ratings of the at-issueness of the prejacent of unembedded EASs.

The at-issueness diagnostic used in Exp.~2 relies on the assumption that at-issue and not-at-issue content differ in the extent to which it is up for debate and can be directly assented/dissented with. For previous uses of diagnostics that rely on this assumption see, e.g., \citealt{amaral-etal07,xue-onea11,murray2014,anderbois-etal2015,destruel-etal2015,tonhauser-sula6} and \citealt{syrett-koev2015}. The diagnostic we use here is the same as that \citepos{tbd-variability} Exps.~2. The 3-turn dialogue in (\ref{sure}) illustrates how the diagnostic was set up on the basis of the appositive content associated with nominal appositives. The speaker of the first turn, Debby, utters an indicative sentence with the target expression, here a nominal appositive, and thereby commits herself to various utterance contents, including the appositive content that Martha's new car is a BMW. The speaker of the second turn, Harry, utters the question {\em Are you sure?}, thereby challenging some content of the first speaker's utterance. In the third turn, Debby utters an indicative sentence in which the content to be diagnosed for at-issueness, here the appositive content of her first utterance, realizes the content of the clausal complement of {\em sure}, thereby identifying it as the content that Debby took the Harry to be challenging.

@@

\caption{Count of ratings, with percentages, according to whether the generalization of the EAS follows from the common ground or is neutral.}\label{t-ai}

@@

We fitted a binomial mixed-effects logistic regression predicting rating (0/no, 1/yes) from a fixed effect of condition (with EAS$_{\mbox{n}}$ as the reference level; 680 data points). The model included the maximal random effects structure justified by the data that allowed the model to converge: random by-adjective intercepts (capturing differences in at-issueness between adjectives).\footnote{A model that predicted rating from condition with a random by-participant intercept (capturing differences in at-issueness rating between participants) also revealed a main effect of condition ($\beta$ = 1.23, $SE$ = 0.23, $z$ = 5.32, $\chi^2$(1) = 27.62, $p <$ .0001).} The analysis was conducted using the lme4 package (\citealt{bates-etal2015}). A log-likelihood comparison of the model with the fixed effect to the model without the fixed effect revealed a significant main effect of EAS type. Specifically, the prejacent of EAS$_{\mbox{f}}$ received more `yes' ratings than the prejacent of EAS$_{\mbox{n}}$ ($\beta$ = 0.56, $SE$ = 0.16, $z$ = 3.57, $\chi^2$(1) = 12.89, $p =$ .0003), indicating that the prejacent of EAS$_{\mbox{f}}$ was judged to be more at-issue than that of EAS$_{\mbox{n}}$. These findings provide empirical support for the analysis developed in section \ref{s3}, which predicts that the prejacent of EASs is more likely to be at-issue when the generalization follows from world knowledge than when it does not.\footnote{The projective content of the four control stimuli in (\ref{proj}) differed in the extent to which they received `no' ratings (indicating not-at-issueness): 94\% (64 of 68) for the appositive content in (\ref{proj}a), 90\% (61 of 68 for the possession content in (\ref{proj}b), 75\% (51 of 68) for the content of the clausal complement of {\em be annoyed} in (\ref{proj}c) and 44\% (30 of 68) for the content of the clausal complement of {\em discover} in (\ref{proj}d). We can compare these findings with the findings reported for similar contents in \citealt{tbd-variability}, whose Exp.~2a used the same diagnostic for at-issueness, but participants gave ratings on a slider. Further differences between the two experiments is that \citealt{tbd-variability} included more than one item for each of the projective contents but only included EASs with {\em stupid}. With these caveats in mind, we can note a similarity in the findings of the two experiments: as in the experiment reported on here, \citet{tbd-variability} found that the possession content and appositive content were most not-at-issue (mean ratings of .83 and .82, respectively), followed by the content of the clausal complement of {\em be annoyed} (mean: .78) and the prejacent of EASs (mean: .7), and finally the content of the clausal complement of {\em discover} (mean .47). These findings provide further support for the hypothesis that the prejacent of EASs overall is not highly not-at-issue.}

@@

\ex The stronger the inference to the truth of the generalization from world knowledge, the higher the at-issueness of the prejacent.

@@

The histogram in Figure \ref{f-dialect} shows the 134 participants' mean projectivity ratings for the two types of NEAS. The right panel reveals that, off the 134 participants, only 23 (17\%) had mean projectivity ratings of at least 6.5 for the NEAS in which the negation of the generalization follows from the common ground; when considering mean projectivity ratings of at least 5.5, this number still only rises to 55 (41\%) participants. Thus, the hypothesis that a majority of native speakers of American English have a lexical entry for evaluative adjectives according to which the prejacent is a lexically-specified presupposition is not supported by the mean certainty ratings of participants in Exp.~1.

>>>>

\newcommand{\jt}[1]{\textbf{\color{blue}JT: #1}}
\newcommand{\jd}[1]{\textbf{\color{green}[jd: #1]}}

@@

There were 26-32 certainty ratings for each of the 59 NEAS (mean: 28.5), except for the five NEASs that appeared on two lists, for which there were 52-58 certainty ratings each (mean: 54). We calculated the mean certainty rating of the prejacent of each NEAS: the lowest mean certainty rating was 1.2, the highest was 6.7 and the mean certainty rating overall was 3.2. Given that participants gave their ratings on a 7-point scale, with the lowest rating (1) indicating that the speaker was not certain about the relevant content and the highest rating (7) indicating that the speaker was certain about the relevant content, this mean certainty rating already suggests that the prejacent of naturally occurring NEAS is not highly projective. Figure \ref{f-corpus} shows the mean certainty ratings of each NEAS by evaluative adjective; darker dots indicate overlapping means. The distribution of mean certainty ratings again suggests that the prejacent of naturally occurring NEAS is projective, but not highly so, and that NEAS in which the prejacent does not project are well-attested in naturally occurring data. These findings provide empirical support for an analysis according to which the prejacent is not lexically specified as a presupposition. \jd{can't they just invoke the `dialect' response here? or did you make sure that each participant saw multiple instances of each adjective, so you can compare whether within subjects ratings differ?}

@@

\caption{Mean certainty rating of 59 naturally occurring NEASs by evaluative adjective. Darker dots indicate overlapping means.\jd{There should be error bars or sth showing the amount of uncertainty around means on this. I couldn't find the code for it or I would have tried sth}}\label{f-corpus}

@@

\begin{exe}
\ex\label{xbox} I was stupid to buy the Xbox 360 elite.\footnote{\url{www.gamespot.com/forums/xbox-association-1000003/i-was-stupid-to-buy-the-xbox-360-elite-26937557}}
\end{exe}

@@

\end{exe}
In the next section, we provide empirical evidence for the analysis. \jd{I would strongly advise against the "providing empirical evidence" framing here and throughout. Perhaps instead: In the next section, we test three predictions made by the analysis.}

\section{Empirical evidence for the analysis\jd{Again, I'd rather say sth like "An empirical test of the analysis"}}\label{s4}

In this section we empirically test three predictions of the analysis of EASs developed in the previous section. The predictions are shown in (\ref{pred}): the prediction in (\ref{pred}a) is derived from (\ref{cq-eval}a), and the predictions in (\ref{pred}b) and (\ref{pred}c) are derived from (\ref{cq-eval}b).

@@

Next we consider examples of NEASs in which the prejacent does not project. Two of the prosodic realization of EASs considered in section \ref{s3331}\jd{?} were such that the EASs have Current Questions that are compatible with Discourse Questions according to which the prejacent is at-issue and therefore does not project: focus on the subject noun phrase and focus on the {\em to}-infinitive. In the examples in (\ref{subj}), the subject noun phrases are plausibly understood to be contrastively focused. A particularly clear example is (\ref{subj}a) where the speaker contrasts themselves with the uncle. Another clear example is (\ref{subj}b): here, {\em either} establishes a contrast between the Google founders and the federal government.

@@

\subsection{Experiment 1: Projectivity of the prejacent}\label{s42}
\jd{this isn't Experiment 1 -- there's already an experiment in this paper. not sure if you deliberately called it exp 1 though, so will hold off on updating all the references to it in the following}

In this section we experimentally test the prediction of our analysis in (\ref{pred}b): the stronger the inference to the truth of the generalization from world knowledge, the less projective the prejacent is.

@@

\caption{Mean projectivity rating for prejacents of NEAS with the 10 evaluative adjectives in the Content condition (left panels) and the Context condition (right panels) by whether the generalization or its negation follow from the common ground. Error bars indicate bootstrapped 95\% confidence intervals.}\label{f-condis}
\end{center}
\end{figure}

We fitted ordinal mixed-effects regression models to the target data in the Content and Context conditions (668 and 672 data points, respectively) \jd{why were these separate models?}, using the {\tt clmm} function of the {\tt ordinal} package (\citealt{Christensen2013}) in {\em R} (\citealt{r}; version 3.2.0). The models predicted projectivity ratings on the 7-point Likert scale from the fixed effect of the discourse status of the generalization (with `generalization follows' as the reference level). The model included the maximal random effects structure justified by the data and the theoretical assumptions: random by-participant intercepts (capturing differences in projectivity between participants) and random by-adjective intercepts (capturing differences in projectivity between evaluative adjectives) \jd{why no random effects for contents?} and random slopes for the discourse status of the generalization by participant and adjective (capturing that the effect of the discourse status may vary across participants and adjectives). Here and in the remainder of the paper, $p$-values were obtained by comparing models via likelihood ratio tests.

@@

\subsection{Experiment 2: At-issueness of the prejacent}\label{s43}
\jd{should be Exp 3}

This experiment tests the prediction in (\ref{pred}c): the stronger the inference to the truth of the generalization from the common ground, the more at-issue the prejacent is. This prediction is explored on the basis of participants' ratings of the at-issueness of the prejacent of unembedded EASs. \jd{the prediction is formulated in quantitative/gradient terms, but the generalization manipulation in the experiment is categorical. revise or am i missing sth?}

The at-issueness diagnostic used in Exp.~2 relies on the assumption that at-issue and not-at-issue content differ in the extent to which it is up for debate and can be directly assented/dissented with. For previous uses of diagnostics that rely on this assumption see, e.g., \citealt{amaral-etal07,xue-onea11,murray2014,anderbois-etal2015,destruel-etal2015,tonhauser-sula6} and \citealt{syrett-koev2015}. The diagnostic we use here is the same as that in \citepos{tbd-variability} Exps.~2. The 3-turn dialogue in (\ref{sure}) illustrates how the diagnostic was set up on the basis of the appositive content associated with nominal appositives. The speaker of the first turn, Debby, utters an indicative sentence with the target expression, here a nominal appositive, and thereby commits herself to various utterance contents, including the appositive content that Martha's new car is a BMW. The speaker of the second turn, Harry, utters the question {\em Are you sure?}, thereby challenging some content of the first speaker's utterance. In the third turn, Debby utters an indicative sentence in which the content to be diagnosed for at-issueness, here the appositive content of her first utterance, realizes the content of the clausal complement of {\em sure}, thereby identifying it as the content that Debby took the Harry to be challenging.

@@

\caption{Count of ratings, with percentages, according to whether the generalization of the EAS follows from the common ground or is neutral.\jd{would make this a plot}}\label{t-ai}

@@

To evaluate the effect of EAS type on at-issueness, we fit a Bayesian binomial mixed effects model with uninformative  priors using the R package \verb|brms| \citep{buerkner2017}. The model predicted the log odds of `yes' over `no' ratings  from a fixed effect of  EAS type (with EAS$_{\mbox{n}}$ as the reference level). We included the maximal random effects structure justified by the design: random intercepts for adjectives \jd{why not for adjective-content combinations?} and participants as well as random by-adjective and by-participant slopes for condition. Four chains converged after 2000 iterations each (warmup = 1000, \(\hat{R}=1\) for all estimated parameters).

The model provided evidence for the predicted effect of EAS type on at-issueness, such that the prejacent of EAS$_{\mbox{f}}$ was more likely to receive a `yes' rating than the prejacent of EAS$_{\mbox{n}}$  ($\beta$ = 1.28, 95\% Credible Interval={[}0.44, 2.11{]}), suggesting that the prejacent of EAS$_{\mbox{f}}$ was judged to be more at-issue than that of EAS$_{\mbox{n}}$.\footnote{In Bayesian mixed effects regression modeling, 95\% credible intervals indicate the range within which we can be certain with probability 0.95 that the parameter estimate $\beta$  lies, given the data at hand and our model (see, for example, Jaynes \& Kempthorne,1976;  Morey, Hoekstra, Rouder, Lee, \& Wagenmakers, 2016).\jd{JT, I'm unsure about how much info to include here and will add citations depending on what we decide to include}} 
%We fitted a binomial mixed-effects logistic regression predicting rating (0/no, 1/yes) from a fixed effect of condition (with EAS$_{\mbox{n}}$ as the reference level; 680 data points). The model included the maximal random effects structure justified by the data that allowed the model to converge: random by-adjective intercepts (capturing differences in at-issueness between adjectives).\footnote{A model that predicted rating from condition with a random by-participant intercept (capturing differences in at-issueness rating between participants) also revealed a main effect of condition ($\beta$ = 1.23, $SE$ = 0.23, $z$ = 5.32, $\chi^2$(1) = 27.62, $p <$ .0001).} The analysis was conducted using the lme4 package (\citealt{bates-etal2015}). A log-likelihood comparison of the model with the fixed effect to the model without the fixed effect revealed a significant main effect of EAS type. Specifically, the prejacent of EAS$_{\mbox{f}}$ received more `yes' ratings than the prejacent of EAS$_{\mbox{n}}$ ($\beta$ = 0.56, $SE$ = 0.16, $z$ = 3.57, $\chi^2$(1) = 12.89, $p =$ .0003), indicating that the prejacent of EAS$_{\mbox{f}}$ was judged to be more at-issue than that of EAS$_{\mbox{n}}$. 
These findings provide empirical support for the analysis developed in section \ref{s3}, which predicts that the prejacent of EASs is more likely to be at-issue when the generalization follows from world knowledge than when it does not.\footnote{The projective content of the four control stimuli in (\ref{proj}) differed in the extent to which they received `no' ratings (indicating not-at-issueness): 94\% (64 of 68) for the appositive content in (\ref{proj}a), 90\% (61 of 68 for the possession content in (\ref{proj}b), 75\% (51 of 68) for the content of the clausal complement of {\em be annoyed} in (\ref{proj}c) and 44\% (30 of 68) for the content of the clausal complement of {\em discover} in (\ref{proj}d). We can compare these findings with the findings reported for similar contents in \citealt{tbd-variability}, whose Exp.~2a used the same diagnostic for at-issueness, but participants gave ratings on a slider. Further differences between the two experiments is that \citealt{tbd-variability} included more than one item for each of the projective contents but only included EASs with {\em stupid}. With these caveats in mind, we can note a similarity in the findings of the two experiments: as in the experiment reported on here, \citet{tbd-variability} found that the possession content and appositive content were most not-at-issue (mean ratings of .83 and .82, respectively), followed by the content of the clausal complement of {\em be annoyed} (mean: .78) and the prejacent of EASs (mean: .7), and finally the content of the clausal complement of {\em discover} (mean .47). These findings provide further support for the hypothesis that the prejacent of EASs overall is not highly not-at-issue.}

@@

\ex The stronger the inference to the truth of the generalization from world knowledge, the higher the at-issueness of the prejacent. \jd{again, the gradient formulation of this is somewhat at odds with the categorical experimental test}

@@

The histogram in Figure \ref{f-dialect} shows the 134 participants' mean projectivity ratings for the two types of NEAS. The right panel reveals that, of the 134 participants, only 23 (17\%) had mean projectivity ratings of at least 6.5 for the NEAS in which the negation of the generalization follows from the common ground; when considering mean projectivity ratings of at least 5.5, this number still only rises to 55 (41\%) participants. Thus, the hypothesis that a majority of native speakers of American English have a lexical entry for evaluative adjectives according to which the prejacent is a lexically-specified presupposition is not supported by the mean certainty ratings of participants in Exp.~1. \jd{I support the point in general, but I'm wary of drawing strong conclusions from assumptions about interpretations of absolute points on these scales...}
